Changes in the justification of educational inequalities. The role of perceptions of inequality and meritocracy during the COVID pandemic.

### 2025-04-17 Title-Page.Rmd
update submit

---
title: "Changes in the justification of educational inequalities. The role of perceptions of inequality and meritocracy during the COVID pandemic. [^*]"
linestretch: '1.5'
output:
  pdf_document:
    toc: false
    number_sections: false
    keep-tex: true
geometry: margin=0.78in
header-includes:
  - \usepackage{times}           # Times New Roman
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage[figurename=Fig.]{caption}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
fontsize: 12pt

---

>>>>

---
title: "Changes in the justification of educational inequalities. The role of perceptions of inequality and meritocracy during the COVID pandemic. [^*]"
linestretch: '1.5'
output:
  pdf_document:
    toc: false
    number_sections: false
    keep_tex: true
geometry: margin=0.78in
header-includes:
  - \usepackage{times}           # Times New Roman
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage[figurename=Fig.]{caption}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
fontsize: 12pt
---

### 2025-04-17 paper.tex
update submit

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
]{article}

@@

\usepackage[noblocks]{authblk}
\renewcommand*{\Authsep}{, }
\renewcommand*{\Authand}{, }
\renewcommand*{\Authands}{, }
\renewcommand\Affilfont{\small}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

~

Model 1

Model 2

Model 3

Model 4

Model 5

Model 6

Model 7

Model 8

Intercept

1.847***

1.853***

1.920***

1.776***

1.641***

1.563***

2.174***

2.183***

~

(0.026)

(0.038)

(0.048)

(0.064)

(0.068)

(0.069)

(0.086)

(0.120)

Wave (Ref.= Wave 2016)

~

~

~

~

~

~

~

~

~

~

~

~

~

~

~

~

~

~~~~~Wave 2017

-0.167***

~

~

~

~

~

~

~

~

(0.029)

~

~

~

~

~

~

~

~~~~~Wave 2018

-0.059*

~

~

~

~

~

~

~

~

(0.029)

~

~

~

~

~

~

~

~~~~~Wave 2019

-0.030

~

~

~

~

~

~

~

~

(0.029)

~

~

~

~

~

~

~

~~~~~Wave 2022

0.204***

~

~

~

~

~

~

~

~

(0.030)

~

~

~

~

~

~

~

~~~~~Wave 2023

0.233***

~

~

~

~

~

~

~

~

(0.029)

~

~

~

~

~

~

~

Wave

~

-0.073***

-0.073***

-0.073***

-0.076***

-0.076***

-0.052**

-0.052**

~

~

(0.020)

(0.020)

(0.020)

(0.020)

(0.020)

(0.020)

(0.020)

Wave\^{}2

~

0.016***

0.016***

0.016***

0.016***

0.016***

0.013***

0.013***

~

~

(0.002)

(0.002)

(0.002)

(0.002)

(0.002)

(0.002)

(0.002)

Covid: receive state benefits

~

~

-0.095*

-0.097*

-0.100*

-0.102*

-0.102**

-0.093*

~

~

~

(0.041)

(0.041)

(0.040)

(0.040)

(0.039)

(0.041)

Covid: economy more important than health

~

~

~

0.065***

0.060**

0.055**

0.049**

0.038*

~

~

~

~

(0.019)

(0.019)

(0.019)

(0.019)

(0.019)

Merit: Talent

~

~

~

~

0.055***

-0.002

-0.003

-0.005

~

~

~

~

~

(0.010)

(0.012)

(0.012)

(0.012)

Merit: Effort

~

~

~

~

~

0.096***

0.084***

0.083***

~

~

~

~

~

~

(0.013)

(0.013)

(0.013)

Inequality perception

~

~

~

~

~

~

-0.135***

-0.134***

~

~

~

~

~

~

~

(0.012)

(0.012)

Universitary (Ref.= Less than universitary)

~

~

~

~

~

~

~

-0.048

~

~

~

~

~

~

~

~

(0.046)

Household income

~

~

~

~

~

~

~

0.001*

~

~

~

~

~

~

~

~

(0.000)

Controls

No

No

No

No

No

No

No

Yes

BIC

29667.072

29670.297

29678.484

29682.436

29668.980

29626.960

29510.881

29626.312

Num. obs.

7576

7576

7576

7576

7576

7576

7576

7576

Num. groups: Individuals

1322

1322

1322

1322

1322

1322

1322

1322

Var: Individuals (Intercept)

0.185

0.184

0.183

0.179

0.174

0.170

0.164

0.159

Var: Residual

0.497

0.500

0.500

0.500

0.499

0.496

0.488

0.488

*** p \textless{} 0.001; ** p \textless{} 0.01; * p \textless{} 0.05.
Note: Model 8 is controlled by age, gender, political position, and
subjective social status.

@@

~

Model 8

Model 9

Model 10

Intercept

2.18***

2.03***

2.09***

~

(0.12)

(0.13)

(0.13)

Wave

-0.05**

-0.05*

-0.05**

~

(0.02)

(0.02)

(0.02)

Wave\^{}2

0.01***

0.01***

0.01***

~

(0.00)

(0.00)

(0.00)

Covid: receive state benefits

-0.09*

0.11

0.03

~

(0.04)

(0.07)

(0.07)

Merit: Talent

-0.00

0.05*

-0.01

~

(0.01)

(0.02)

(0.01)

Merit: Effort

0.08***

0.08***

0.12***

~

(0.01)

(0.01)

(0.02)

Receive state benefits * Merit: Talent

~

-0.07**

~

~

~

(0.02)

~

Receive state benefits * Merit: Effort

~

~

-0.05*

~

~

~

(0.02)

BIC

29626.31

29630.35

29636.59

Num. obs.

7576

7576

7576

Num. groups: Individuals

1322

1322

1322

Var: Individuals (Intercept)

0.16

0.16

0.16

Var: Residual

0.49

0.49

0.49

\item *

** p \textless{} 0.001; ** p \textless{} 0.01; * p \textless{} 0.05.
Note: All the models are controlled by educational level, income
quintile, subjective social status, age, gender, political position, and
inequality perception

@@

~

Model 1

Model 2

Model 3

Model 4

Model 5

Model 6

Model 7

Intercept

1.847***

1.853***

1.873***

1.741***

1.664***

2.276***

2.277***

~

(0.026)

(0.038)

(0.090)

(0.092)

(0.092)

(0.105)

(0.138)

Wave (Ref.= Wave 2016)

~

~

~

~

~

~

~

~

~

~

~

~

~

~

~

~~~~~Wave 2017

-0.167***

~

~

~

~

~

~

~

(0.029)

~

~

~

~

~

~

~~~~~Wave 2018

-0.059*

~

~

~

~

~

~

~

(0.029)

~

~

~

~

~

~

~~~~~Wave 2019

-0.030

~

~

~

~

~

~

~

(0.029)

~

~

~

~

~

~

~~~~~Wave 2022

0.204***

~

~

~

~

~

~

~

(0.030)

~

~

~

~

~

~

~~~~~Wave 2023

0.233***

~

~

~

~

~

~

~

(0.029)

~

~

~

~

~

~

Wave

~

-0.073***

-0.073***

-0.076***

-0.076***

-0.052**

-0.052**

~

~

(0.020)

(0.020)

(0.020)

(0.020)

(0.020)

(0.020)

Wave\^{}2

~

0.016***

0.016***

0.016***

0.016***

0.013***

0.013***

~

~

(0.002)

(0.002)

(0.002)

(0.002)

(0.002)

(0.002)

Covid: receive state benefits

~

~

-0.097*

-0.100*

-0.102*

-0.102**

-0.093*

~

~

~

(0.041)

(0.040)

(0.040)

(0.039)

(0.041)

Covid: economy more important than health

~

~

0.065***

0.060**

0.055**

0.049**

0.038*

~

~

~

(0.019)

(0.019)

(0.019)

(0.019)

(0.019)

Merit: Talent

~

~

~

0.055***

-0.002

-0.003

-0.005

~

~

~

~

(0.010)

(0.012)

(0.012)

(0.012)

Merit: Effort

~

~

~

~

0.096***

0.084***

0.083***

~

~

~

~

~

(0.013)

(0.013)

(0.013)

Inequality perception

~

~

~

~

~

-0.135***

-0.134***

~

~

~

~

~

~

(0.012)

(0.012)

Universitary (Ref.= Less than universitary)

~

~

~

~

~

~

-0.048

~

~

~

~

~

~

~

(0.046)

Household Income

~

~

~

~

~

~

0.001*

~

~

~

~

~

~

~

(0.000)

Subjective Social Status

~

~

~

~

~

~

-0.005

~

~

~

~

~

~

~

(0.012)

Age (Ref.= 18-29)

~

~

~

~

~

~

~

~

~

~

~

~

~

~

~

~~~~~Age 30-49

~

~

~

~

~

~

-0.033

~

~

~

~

~

~

~

(0.051)

~~~~~Age 50-64

~

~

~

~

~

~

0.009

~

~

~

~

~

~

~

(0.053)

~~~~~Age 65 or more

~

~

~

~

~

~

0.123

~

~

~

~

~

~

~

(0.066)

Gender (Ref. Male)

~

~

~

~

~

~

-0.082*

~

~

~

~

~

~

~

(0.037)

Pol. pos (Ref.= Left)

~

~

~

~

~

~

~

~

~

~

~

~

~

~

~

~~~~~Center

~

~

~

~

~

~

0.095

~

~

~

~

~

~

~

(0.051)

~~~~~Right

~

~

~

~

~

~

0.220***

~

~

~

~

~

~

~

(0.059)

~~~~~Does not identify

~

~

~

~

~

~

0.085

~

~

~

~

~

~

~

(0.047)

BIC

29667.072

29670.297

29682.436

29668.980

29626.960

29510.881

29626.312

Num. obs.

7576

7576

7576

7576

7576

7576

7576

Num. groups: Individuals

1322

1322

1322

1322

1322

1322

1322

Var: Individuals (Intercept)

0.185

0.184

0.179

0.174

0.170

0.164

0.159

Var: Residual

0.497

0.500

0.500

0.499

0.496

0.488

0.488

*** p \textless{} 0.001; ** p \textless{} 0.01; * p \textless{} 0.05.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  10pt]{article}

@@

\usepackage[noblocks]{authblk}
\renewcommand*{\Authsep}{, }
\renewcommand*{\Authand}{, }
\renewcommand*{\Authands}{, }
\renewcommand\Affilfont{\small}
\renewcommand\Affilfont{\small}
\usepackage{mathptmx} % Times
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

\caption{}
\begin{center}
\scalebox{0.765}{
\begin{tabular}{l c c c c c c c c}
\hline
 & Model 1 & Model 2 & Model 3 & Model 4 & Model 5 & Model 6 & Model 7 & Model 8 \\
\hline
Intercept                                   & $1.847^{***}$  & $1.853^{***}$  & $1.920^{***}$  & $1.776^{***}$  & $1.641^{***}$  & $1.563^{***}$  & $2.174^{***}$  & $2.183^{***}$  \\
                                            & $(0.026)$      & $(0.038)$      & $(0.048)$      & $(0.064)$      & $(0.068)$      & $(0.069)$      & $(0.086)$      & $(0.120)$      \\
Wave (Ref.= Wave 2016)                      &                &                &                &                &                &                &                &                \\
                                            &                &                &                &                &                &                &                &                \\
\quad Wave 2017                             & $-0.167^{***}$ &                &                &                &                &                &                &                \\
                                            & $(0.029)$      &                &                &                &                &                &                &                \\
\quad Wave 2018                             & $-0.059^{*}$   &                &                &                &                &                &                &                \\
                                            & $(0.029)$      &                &                &                &                &                &                &                \\
\quad Wave 2019                             & $-0.030$       &                &                &                &                &                &                &                \\
                                            & $(0.029)$      &                &                &                &                &                &                &                \\
\quad Wave 2022                             & $0.204^{***}$  &                &                &                &                &                &                &                \\
                                            & $(0.030)$      &                &                &                &                &                &                &                \\
\quad Wave 2023                             & $0.233^{***}$  &                &                &                &                &                &                &                \\
                                            & $(0.029)$      &                &                &                &                &                &                &                \\
Wave                                        &                & $-0.073^{***}$ & $-0.073^{***}$ & $-0.073^{***}$ & $-0.076^{***}$ & $-0.076^{***}$ & $-0.052^{**}$  & $-0.052^{**}$  \\
                                            &                & $(0.020)$      & $(0.020)$      & $(0.020)$      & $(0.020)$      & $(0.020)$      & $(0.020)$      & $(0.020)$      \\
Wave$^2$                                    &                & $0.016^{***}$  & $0.016^{***}$  & $0.016^{***}$  & $0.016^{***}$  & $0.016^{***}$  & $0.013^{***}$  & $0.013^{***}$  \\
                                            &                & $(0.002)$      & $(0.002)$      & $(0.002)$      & $(0.002)$      & $(0.002)$      & $(0.002)$      & $(0.002)$      \\
Covid: receive state benefits               &                &                & $-0.095^{*}$   & $-0.097^{*}$   & $-0.100^{*}$   & $-0.102^{*}$   & $-0.102^{**}$  & $-0.093^{*}$   \\
                                            &                &                & $(0.041)$      & $(0.041)$      & $(0.040)$      & $(0.040)$      & $(0.039)$      & $(0.041)$      \\
Covid: economy more important than health   &                &                &                & $0.065^{***}$  & $0.060^{**}$   & $0.055^{**}$   & $0.049^{**}$   & $0.038^{*}$    \\
                                            &                &                &                & $(0.019)$      & $(0.019)$      & $(0.019)$      & $(0.019)$      & $(0.019)$      \\
Merit: Talent                               &                &                &                &                & $0.055^{***}$  & $-0.002$       & $-0.003$       & $-0.005$       \\
                                            &                &                &                &                & $(0.010)$      & $(0.012)$      & $(0.012)$      & $(0.012)$      \\
Merit: Effort                               &                &                &                &                &                & $0.096^{***}$  & $0.084^{***}$  & $0.083^{***}$  \\
                                            &                &                &                &                &                & $(0.013)$      & $(0.013)$      & $(0.013)$      \\
Inequality perception                       &                &                &                &                &                &                & $-0.135^{***}$ & $-0.134^{***}$ \\
                                            &                &                &                &                &                &                & $(0.012)$      & $(0.012)$      \\
Universitary (Ref.= Less than universitary) &                &                &                &                &                &                &                & $-0.048$       \\
                                            &                &                &                &                &                &                &                & $(0.046)$      \\
Household income                            &                &                &                &                &                &                &                & $0.001^{*}$    \\
                                            &                &                &                &                &                &                &                & $(0.000)$      \\
\hline
Controls                                    & No             & No             & No             & No             & No             & No             & No             & Yes            \\
BIC                                         & $29667.072$    & $29670.297$    & $29678.484$    & $29682.436$    & $29668.980$    & $29626.960$    & $29510.881$    & $29626.312$    \\
Num. obs.                                   & $7576$         & $7576$         & $7576$         & $7576$         & $7576$         & $7576$         & $7576$         & $7576$         \\
Num. groups: Individuals                    & $1322$         & $1322$         & $1322$         & $1322$         & $1322$         & $1322$         & $1322$         & $1322$         \\
Var: Individuals (Intercept)                & $0.185$        & $0.184$        & $0.183$        & $0.179$        & $0.174$        & $0.170$        & $0.164$        & $0.159$        \\
Var: Residual                               & $0.497$        & $0.500$        & $0.500$        & $0.500$        & $0.499$        & $0.496$        & $0.488$        & $0.488$        \\
\hline
\multicolumn{9}{l}{\scriptsize{*** p < 0.001; ** p < 0.01; * p < 0.05.
Note: Model 8 is controlled by age, gender, political position, and subjective social status.}}
\end{tabular}
\label{table:coefficients}
\end{center}

@@

\caption{}
\begin{center}
\scalebox{0.765}{
\begin{tabular}{l c c c}
\toprule
 & Model 8 & Model 9 & Model 10 \\
\midrule
Intercept                              & $2.18^{***}$ & $2.03^{***}$ & $2.09^{***}$ \\
                                       & $(0.12)$     & $(0.13)$     & $(0.13)$     \\
Wave                                   & $-0.05^{**}$ & $-0.05^{*}$  & $-0.05^{**}$ \\
                                       & $(0.02)$     & $(0.02)$     & $(0.02)$     \\
Wave$^2$                               & $0.01^{***}$ & $0.01^{***}$ & $0.01^{***}$ \\
                                       & $(0.00)$     & $(0.00)$     & $(0.00)$     \\
Covid: receive state benefits          & $-0.09^{*}$  & $0.11$       & $0.03$       \\
                                       & $(0.04)$     & $(0.07)$     & $(0.07)$     \\
Merit: Talent                          & $-0.00$      & $0.05^{*}$   & $-0.01$      \\
                                       & $(0.01)$     & $(0.02)$     & $(0.01)$     \\
Merit: Effort                          & $0.08^{***}$ & $0.08^{***}$ & $0.12^{***}$ \\
                                       & $(0.01)$     & $(0.01)$     & $(0.02)$     \\
Receive state benefits * Merit: Talent &              & $-0.07^{**}$ &              \\
                                       &              & $(0.02)$     &              \\
Receive state benefits * Merit: Effort &              &              & $-0.05^{*}$  \\
                                       &              &              & $(0.02)$     \\
\midrule
BIC                                    & $29626.31$   & $29630.35$   & $29636.59$   \\
Num. obs.                              & $7576$       & $7576$       & $7576$       \\
Num. groups: Individuals               & $1322$       & $1322$       & $1322$       \\
Var: Individuals (Intercept)           & $0.16$       & $0.16$       & $0.16$       \\
Var: Residual                          & $0.49$       & $0.49$       & $0.49$       \\
\bottomrule
\multicolumn{4}{l}{\scriptsize{*** p < 0.001; ** p < 0.01; * p < 0.05. 
Note: All the models are controlled by educational level, income quintile, subjective social status, age, gender, political position, and inequality perception}}
\end{tabular}
}
\label{table:coefficients}
\end{center}

@@

\caption{}
\begin{center}
\scalebox{0.765}{
\begin{tabular}{l c c c c c c c}
\hline
 & Model 1 & Model 2 & Model 3 & Model 4 & Model 5 & Model 6 & Model 7 \\
\hline
Intercept                                   & $1.847^{***}$  & $1.853^{***}$  & $1.873^{***}$  & $1.741^{***}$  & $1.664^{***}$  & $2.276^{***}$  & $2.277^{***}$  \\
                                            & $(0.026)$      & $(0.038)$      & $(0.090)$      & $(0.092)$      & $(0.092)$      & $(0.105)$      & $(0.138)$      \\
Wave (Ref.= Wave 2016)                      &                &                &                &                &                &                &                \\
                                            &                &                &                &                &                &                &                \\
\quad Wave 2017                             & $-0.167^{***}$ &                &                &                &                &                &                \\
                                            & $(0.029)$      &                &                &                &                &                &                \\
\quad Wave 2018                             & $-0.059^{*}$   &                &                &                &                &                &                \\
                                            & $(0.029)$      &                &                &                &                &                &                \\
\quad Wave 2019                             & $-0.030$       &                &                &                &                &                &                \\
                                            & $(0.029)$      &                &                &                &                &                &                \\
\quad Wave 2022                             & $0.204^{***}$  &                &                &                &                &                &                \\
                                            & $(0.030)$      &                &                &                &                &                &                \\
\quad Wave 2023                             & $0.233^{***}$  &                &                &                &                &                &                \\
                                            & $(0.029)$      &                &                &                &                &                &                \\
Wave                                        &                & $-0.073^{***}$ & $-0.073^{***}$ & $-0.076^{***}$ & $-0.076^{***}$ & $-0.052^{**}$  & $-0.052^{**}$  \\
                                            &                & $(0.020)$      & $(0.020)$      & $(0.020)$      & $(0.020)$      & $(0.020)$      & $(0.020)$      \\
Wave$^2$                                    &                & $0.016^{***}$  & $0.016^{***}$  & $0.016^{***}$  & $0.016^{***}$  & $0.013^{***}$  & $0.013^{***}$  \\
                                            &                & $(0.002)$      & $(0.002)$      & $(0.002)$      & $(0.002)$      & $(0.002)$      & $(0.002)$      \\
Covid: receive state benefits               &                &                & $-0.097^{*}$   & $-0.100^{*}$   & $-0.102^{*}$   & $-0.102^{**}$  & $-0.093^{*}$   \\
                                            &                &                & $(0.041)$      & $(0.040)$      & $(0.040)$      & $(0.039)$      & $(0.041)$      \\
Covid: economy more important than health   &                &                & $0.065^{***}$  & $0.060^{**}$   & $0.055^{**}$   & $0.049^{**}$   & $0.038^{*}$    \\
                                            &                &                & $(0.019)$      & $(0.019)$      & $(0.019)$      & $(0.019)$      & $(0.019)$      \\
Merit: Talent                               &                &                &                & $0.055^{***}$  & $-0.002$       & $-0.003$       & $-0.005$       \\
                                            &                &                &                & $(0.010)$      & $(0.012)$      & $(0.012)$      & $(0.012)$      \\
Merit: Effort                               &                &                &                &                & $0.096^{***}$  & $0.084^{***}$  & $0.083^{***}$  \\
                                            &                &                &                &                & $(0.013)$      & $(0.013)$      & $(0.013)$      \\
Inequality perception                       &                &                &                &                &                & $-0.135^{***}$ & $-0.134^{***}$ \\
                                            &                &                &                &                &                & $(0.012)$      & $(0.012)$      \\
Universitary (Ref.= Less than universitary) &                &                &                &                &                &                & $-0.048$       \\
                                            &                &                &                &                &                &                & $(0.046)$      \\
Household Income                            &                &                &                &                &                &                & $0.001^{*}$    \\
                                            &                &                &                &                &                &                & $(0.000)$      \\
Subjective Social Status                    &                &                &                &                &                &                & $-0.005$       \\
                                            &                &                &                &                &                &                & $(0.012)$      \\
Age (Ref.= 18-29)                           &                &                &                &                &                &                &                \\
                                            &                &                &                &                &                &                &                \\
\quad Age 30-49                             &                &                &                &                &                &                & $-0.033$       \\
                                            &                &                &                &                &                &                & $(0.051)$      \\
\quad Age 50-64                             &                &                &                &                &                &                & $0.009$        \\
                                            &                &                &                &                &                &                & $(0.053)$      \\
\quad Age 65 or more                        &                &                &                &                &                &                & $0.123$        \\
                                            &                &                &                &                &                &                & $(0.066)$      \\
Gender (Ref. Male)                          &                &                &                &                &                &                & $-0.082^{*}$   \\
                                            &                &                &                &                &                &                & $(0.037)$      \\
Pol. pos (Ref.= Left)                       &                &                &                &                &                &                &                \\
                                            &                &                &                &                &                &                &                \\
\quad Center                                &                &                &                &                &                &                & $0.095$        \\
                                            &                &                &                &                &                &                & $(0.051)$      \\
\quad Right                                 &                &                &                &                &                &                & $0.220^{***}$  \\
                                            &                &                &                &                &                &                & $(0.059)$      \\
\quad Does not identify                     &                &                &                &                &                &                & $0.085$        \\
                                            &                &                &                &                &                &                & $(0.047)$      \\
\hline
BIC                                         & $29667.072$    & $29670.297$    & $29682.436$    & $29668.980$    & $29626.960$    & $29510.881$    & $29626.312$    \\
Num. obs.                                   & $7576$         & $7576$         & $7576$         & $7576$         & $7576$         & $7576$         & $7576$         \\
Num. groups: Individuals                    & $1322$         & $1322$         & $1322$         & $1322$         & $1322$         & $1322$         & $1322$         \\
Var: Individuals (Intercept)                & $0.185$        & $0.184$        & $0.179$        & $0.174$        & $0.170$        & $0.164$        & $0.159$        \\
Var: Residual                               & $0.497$        & $0.500$        & $0.500$        & $0.499$        & $0.496$        & $0.488$        & $0.488$        \\
\hline
\multicolumn{8}{l}{\scriptsize{*** p < 0.001; ** p < 0.01; * p < 0.05.}}
\end{tabular}
\label{table:coefficients}
\end{center}
